Linear instability underlying synchronous waving of marine grass in flow

### 2014-09-03 Paper/grass.tex
abstact update september 3rd

%The spontaneous waving of marine grass is thought to be due to a Kelvin-Helmholtz instability resulting from an inflection point near the canopy top in the flow profile.
We study the mechanism behind synchronous waving of marine grass, known as Mo-nami. We do linear stability analysis of a mathematical model which considers grass to exert a continuum drag on the flow.
Our analysis of flow through grass bed predicts a critical threshold condition for instability and associated waving frequency
which compares well with experimental observations. Our analysis further predicts two distinct mode of instability which might lead to Mo-nami.
One of these mode shares many characteristics with the Kelvin-Helmholtz instability, we termed this mode as ``Mode 1''. The other mode can be thought of as instability of 
inviscid flow above grass coupled with the porous flow through grass bed, we refer to this mode as ``Mode 2''.  In the limit of dense grass bed these two modes can be asymptotically 
distinguished. In the parameter regime typical of marine grass beds, the two modes merge and are indistinguishable.

>>>>

%The spontaneous waving of marine grass is thought to be due to a Kelvin-Helmholtz instability resulting from an inflection point near the canopy top in the flow profile.
We study the mechanism behind Mo-nami, a phenomenon associated with the synchronous waving of marine grass. Flow through grass bed gives rise to a region of strong shear near tip of grass 
known as shear layer, due to vertical discontinuity of grass drag. Linear stability analysis of a mathematical model incorporating grass drag as a continuum field has been 
carried out. Our analysis predicts a critical threshold condition for flow instability leading to Mo-nami and associated waving frequency
which compares well with experimental observations. Further analysis predicts existence of two distinct mode of instability.
One of these mode has many characteristics similar to the Kelvin-Helmholtz instability where shear layer plays a central role, we termed this as ``Mode 1''. 
The other mode can be interpreted as instability of 
inviscid flow through a grass bed where shear layer doesn't play a critical role, we refer this as ``Mode 2''. In the limit of dense grass bed these two modes can be
distinguished. For the parameter regime typical of marine grass beds, the two modes merge and are indistinguishable.
